Glucose ingestion before and after resistance training does not augment ribosome biogenesis in healthy moderately trained young adults

### 2023-09-28 ejap.manuscript.RMD
working on references

---
title: ""
author: ""
bibliography: resources/ribose-paper.bib
csl: resources/jap.csl
output:
  word_document:
    reference_docx: resources/reference-template-02.docx
editor_options: 
  chunk_output_type: console
---

@@

@@

# AUTHOR CONTRIBUTIONS
Conceived and designed research: SE, HH, DH.
Performed experiments: KL, DH, HH, HN, SCM.
Interpreted results of experiments: KL, DH.
Prepared Figures: KL, DH.
Drafted manuscripts: KL, DH.
Edited and revised manuscript: SE, HH, DH.
Approved final version of the manuscript: .

# References

>>>>

---
title: ""
author: ""
bibliography: resources/ribose-paper.bib
csl: resources/ejap.csl
output:
  word_document:
    reference_docx: resources/reference-template-02.docx
editor_options: 
  chunk_output_type: console
---

@@

## AUTHOR CONTRIBUTIONS

Data was collected at the sports science lab at the Inland Norway University of Applied Sciences, with all analyses except for serum blood samples were performed at the university. Serum blood samples were performed at Innlandet Hospital Trust. S.E., H.H. and D.H. conceived and designed the study; K.L., S.C.M., D.H. and H.H. performed experiements; K.L. and D.H. interpreted the results; K.L. and D.H. prepared figures; K.L. drafted the manuscript; D.H., H.H. and S.E. edited and revised the manuscript; D.H., H.H. and S.E. approved the final version of the manuscript.

## Acknowledgements
Gratitude are in order to Henriette Spilhaug Bollandsås, Nora Lerdalen Bonsak and Thea Bøhn Nyløkken for their dedication and hard work in the training intervention. The authors would also like to express their gratitude to all the participants, staying commited to this demanding protocol in an impressive way. We also thank Håvard Nygaard for lending your expertise and technical skills to improve this project.

@@

## References
